Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-10 ms.tex
updated PCA model plots and added software citations.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.3\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.3\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.3\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Bottom) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

We also perform PCA along the time axis.
This gives the principal components shown in Figure \ref{fig:PCAtime}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_time_direction.pdf}
\caption{Principal components for orbital phase when working along the time axis.}\label{fig:PCAtime}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
\caption{Time Series of phase shifts.}\label{fig:phaseShift}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using the average light curve (Middle).
(Right) The residuals show significant deviations at phases of -0.5 and 0.05.
}\label{fig:riverPlots}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Right) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

@@

%\begin{figure*}[!hbtp]
%\begin{centering}
%\includegraphics[width=0.99\textwidth]{images/kepler/phase_shifts.pdf}
%\caption{Time Series of phase shifts.}\label{fig:phaseShift}
%\end{centering}
%\end{figure*}
%
%
%\begin{figure*}[!hbtp]
%\begin{centering}
%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shift_vs_amplitude.pdf}
%\includegraphics[width=0.49\textwidth]{images/kepler/phase_shifts_periodogram.pdf}
%\caption{Phase shifts versus amplitude (left) and phase shift periodogram (right).}\label{fig:phaseShift}
%\end{centering}
%\end{figure*}
